Analysis paper

### 2022-05-30 analysis/analysis.Rmd
correct Figure

basline_forecasts <- truth_data %>%
  mutate(difference = c(NA, diff(log(pmax(true_value, 1)))), 
         target_end_date = as.Date(target_end_date), 
         id = 1:n()) %>%
  rowwise() %>%
  mutate(sd = sd(d$difference[pmax(0, id - (4:1))]), 
         quantile = list(qs)) %>%
  tidyr::unnest(cols = quantile) %>%
  mutate(prediction = exp(qnorm(quantile, mean = log(true_value), sd = sd)), 
         model = "Baseline", 
         forecast_date = target_end_date + 2) %>%
  unique()

plot_df <- prediction_data %>%
  filter(model == "Crowd forecast", 
         quantile %in% qs, 
         grepl("2", target)) %>%
  unique() %>%
  rbind(basline_forecasts, fill = TRUE) %>%
  filter(forecast_date %in% forecast_dates$unfiltered) %>%
  pivot_wider(names_from = quantile, values_from = prediction) %>%
  rename(Model = model) %>%
  mutate(target_type = ifelse(target_type == "case", "Case", "Death"))

>>>>

baseline_forecasts <- truth_data %>%
  mutate(log_true_value = log(pmax(true_value, 1)),
         difference = c(NA, diff(log_true_value)), 
         target_end_date = as.Date(target_end_date))

calc_baseline <- function(baseline_forecasts) {
  baseline_forecasts %>%
    mutate(id = 1:n()) %>%
    rowwise() %>%
    mutate(sd = sd(baseline_forecasts$difference[pmax(0, id - (4:1))]), 
           quantile = list(qs)) %>%
    tidyr::unnest(cols = quantile) %>%
    mutate(prediction = exp(qnorm(quantile, mean = log(true_value), sd = sd)), 
           model = "Baseline", 
           forecast_date = target_end_date + 2) %>%
    unique()
}

baseline_forecasts <- 
  rbind(
    calc_baseline(filter(baseline_forecasts, location_name == "Germany" & target_type == "case")), 
    calc_baseline(filter(baseline_forecasts, location_name == "Germany" & target_type == "death")), 
    calc_baseline(filter(baseline_forecasts, location_name == "Poland" & target_type == "case")), 
    calc_baseline(filter(baseline_forecasts, location_name == "Poland" & target_type == "death"))
  )

plot_df <- prediction_data %>%
  filter(model == "Crowd forecast", 
         quantile %in% qs, 
         grepl("2", target)) %>%
  unique() %>%
  rbind(baseline_forecasts, fill = TRUE) %>%
  filter(forecast_date %in% forecast_dates$unfiltered) %>%
  pivot_wider(names_from = quantile, values_from = prediction) %>%
  rename(Model = model) %>%
  mutate(target_type = ifelse(target_type == "case", "Case", "Death"))
